Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors

### 2019-03-21 paper/ms.tex
remove whitespace at end of lines
Fix Ni-56 typesetting.

The ADR scheme describes the consumption of C and the subsequent stages
are described by separate progress variables and
separate relaxation times derived from full nuclear network calculations
\cite{Caldetal07,townetal2016}. In both the quasi-equilibrium and full equilibrium,
the creation of light elements by photodisintegration balances the creation of heavy
elements by fusion, maintaining the equilibrium. The relative balance depends on
thermodynamic conditions, e.g.\ density and temperature, and hydrodynamic motion
during the explosion changes the thermodynamic conditions and thus the
balance.
{\color{blue} Electron capture also influences the evolution in several ways by
neutronizing the material, which produces more neutron rich iron-group
material at the expense of \Ni. Neutronization also shifts the binding
energy of the material and the Fermi energy of electrons, respectively
changing the temperature (due to released energy) and the pressure.
Finally, individual electron capture reactions emit neutrinos that
escape and remove energy from the system.}
Like the input flame speed, the burning model includes tabulated rates for these effects
from detailed NSE calculations ~\citep{SeitTownetal09}. Accordingly, the burning
model is able to describe dynamic evolution of the ash in addition to the
stages of C-O-Ne burning.

>>>>

The ADR scheme describes the consumption of C and the subsequent stages
are described by separate progress variables and
separate relaxation times derived from full nuclear network calculations
\cite{Caldetal07,townetal2016}. In both the quasi-equilibrium and full equilibrium,
the creation of light elements by photodisintegration balances the creation of heavy
elements by fusion, maintaining the equilibrium. The relative balance depends on
thermodynamic conditions, e.g.\ density and temperature, and hydrodynamic motion
during the explosion changes the thermodynamic conditions and thus the
balance.
{\color{blue} Electron capture also influences the evolution in several ways by
neutronizing the material, which produces more neutron rich iron-group
material at the expense of \Ni{56}. Neutronization also shifts the binding
energy of the material and the Fermi energy of electrons, respectively
changing the temperature (due to released energy) and the pressure.
Finally, individual electron capture reactions emit neutrinos that
escape and remove energy from the system.}
Like the input flame speed, the burning model includes tabulated rates for these effects
from detailed NSE calculations ~\citep{SeitTownetal09}. Accordingly, the burning
model is able to describe dynamic evolution of the ash in addition to the
stages of C-O-Ne burning.
